Analysing the factors influencing the wages of the US workforce

### 2024-11-26 paper/paper.qmd
add Datasheet

---
title: "Analysing the factors influencing the wages of the US workforce"
subtitle: "Education as the Strongest Factor While Gender and Race Reflect Inequalities"
author: 
  - Jianing Li
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: today
date-format: long
abstract: "This study uses a multiple linear regression model to analyze key factors influencing wages among the U.S. workforce, including education, age, gender, race, region, and hours worked. The results show that education is the strongest factor, with higher levels of education leading to significantly higher wages, while gender and race reveal notable disparities, with men and Asian workers earning the most. The study also finds a nonlinear relationship between age and wages, with region and hours worked playing smaller but significant roles. By identifying these drivers, the research provides evidence to inform policies aimed at reducing wage gaps and promoting fairer economic outcomes."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

This paper provides a comprehensive analysis of income inequality by examining its key drivers and impacts. @sec-data describes the dataset in detail, highlights its main features, and uses visualizations to present the analysis results. @sec-model focuses on the construction of the multiple linear regression model, validates its effectiveness, and presents the results of the analysis. @sec-discussion analyzes the research findings, explores the reasons behind the observed patterns, and offers policy recommendations to address income inequality. It also identifies the study’s limitations and suggests directions for future research. @sec-appendix provides additional details on the data, model, and methods of survey and sampling, offering more comprehensive support for the study.

@@

# Additional data details

# Model details {#sec-model-details}

>>>>

---
title: "Analysing the factors influencing the wages of the US workforce"
subtitle: "Education as the Strongest Factor While Gender and Race Reflect Inequalities"
author: 
  - Jianing Li
thanks: "Code and data are available at: https://github.com/JianingLi1225/Determinants-of-Wages.git"
date: today
date-format: long
abstract: "This study uses a multiple linear regression model to analyze key factors influencing wages among the U.S. workforce, including education, age, gender, race, region, and hours worked. The results show that education is the strongest factor, with higher levels of education leading to significantly higher wages, while gender and race reveal notable disparities, with men and Asian workers earning the most. The study also finds a nonlinear relationship between age and wages, with region and hours worked playing smaller but significant roles. By identifying these drivers, the research provides evidence to inform policies aimed at reducing wage gaps and promoting fairer economic outcomes."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

This paper provides a comprehensive analysis of income inequality by examining its key drivers and impacts. @sec-data describes the dataset in detail, highlights its main features, and uses visualizations to present the analysis results. @sec-model focuses on the construction of the multiple linear regression model, validates its effectiveness, and presents the results of the analysis. @sec-discussion analyzes the research findings, explores the reasons behind the observed patterns, and offers policy recommendations to address income inequality. It also identifies the study’s limitations and suggests directions for future research. @sec-appendix provides additional details on the model, and methods of survey and sampling, offering more comprehensive support for the study.

@@

## Model details {#sec-model-details}
